Universal Anonymous Signatures

### 2022-06-07 prism-backend/research/gsac/model-uas.tex
Updated sign-unforgeability proof.

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given global system
  parameters \parm, and function \finsp, an opener runs \OKeyGen to generate
  its opening key pair. The function \finsp defines the type of utility that
  will be extractable from signatures.
\item[$\UKeyGen(\parm) \rightarrow \usk$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle
  \Obtain(\usk,\ipk,\scred,\attrs),
  \Issue(\isk,\sipk,\attrs))
  \rangle \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.] %
  This interactive protocol lets a user with key \usk running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of credentials \scred,
  each with a matching issuer key in \sipk.
  The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential.
\item[$\Sign(\usk,\opk,\scred,\msg,\feval) \rightarrow (\sig,\yeval,\ceval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \scred, a message \msg and evaluation
  function \feval, returns signature \sig, a plaintext value \yeval,
  and an encrypted value \ceval. For readability, we use \Sig to denote
  the tuple $(\sig,\yeval,\ceval)$.
\item[$\Verify(\opk, \sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval,\ceval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\sig,\yeval,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $(\sig,
  \yeval)$ over message \msg and evaluation function \feval, generated using
  credentials issued by the issuers with public keys in \sipk. If \sig is valid,
  the function outputs a value $\yinsp$.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval,\ceval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

\begin{description}
\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\attrs_{\scred},\scred)$.]
  Receives an $\langle \Obtain, \Issue \rangle$ transcript, and returns the
  credentials (if any) and their attributes that were involved
  in the request. It clearly needs an honest issuer as, otherwise, the
  transcripts won't be available. Consequently, we only use it to define the
  properties that require an honest issuer.
\item[$\ExtractSign(\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
  \scred,\attrs_{\scred},\yinsp)$.] Receives a signature \Sig,
  as well as the opener identifier \oid, and the identifiers of all issuers of
  the credentials used to produce the signature over \msg, and for \feval. It
  outputs the user secret key and credentials (with their attributes) used to
  generate the signature, and the value returned by the opening fuction.
\item[$\IdentifyCred(\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
  issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
  Otherwise, it returns $0$. In order to be meaningful, this requires that,
  for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
  \IdentifyCred return $1$.
\item[$\IdentifyUK(\uid,\usk)$.] Returns $1$ is \usk is {\uid}'s secret key.
  This is trivial for honest users, for which there must be a one-to-one
  relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
  to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
  to \uid, extract the used secret key, and check if there is a match. Note that
  this does not guarantee that there will be only one \usk per corrupt \uid,
  though. Also, when used for corrupt users, this can only be used when the
  issuer is honest, as transcripts are needed. 
\end{description}

@@

        \procedure{$\ISSUE(\cid,\uid,\iid,\attrs,\siid)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\          
          \pcif \iid \notin \HI: \pcreturn \bot \\
          %\pcif \exists \iid' \in \ISR[\scid] \notin \HI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, 
          \Issue(\PRVIK[\iid],\siid,\attrs) \rangle \\
          \trans[\cid] \gets \utrans \\
          \CRED[\cid] \gets (\uid, \cdot, \iid, \attrs, \cdot, \siid) \\
          \pcreturn \top \\          
        }

        \procedure{$\OBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          %\pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\CRED[\scid],\attrs),\adv \rangle \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
          \pcreturn \top \\
        }

        \procedure{$\CHALb(\oid,\cuid_{0,1},\cscid_{0,1},\msg,\feval)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \oid \in \CO: \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\          
          (\yeval,\cdot) \gets \feval(\UK[\cuid_0],\CRED[\cscid_0],\msg) \\
          ({\yeval}',\cdot) \gets \feval(\UK[\cuid_1],\CRED[\cscid_1],\msg) \\
          \pcif \yeval \neq {\yeval}': \pcreturn \bot \\
          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
          \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
          \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b})
          \rbrace \\
          \pcreturn \cSig_b
        }

@@

        \procedure{$\OBTISS(\cid,\uid,\iid,\attrs,\scid)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \HI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          %\pcif \exists \iid' \in \ISR[\scid]~\st~\iid' \notin \HI: \pcreturn \bot \\
          %\pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot:
          \pcreturn \bot \\
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\UK[\uid],\CRED[\scid],\attrs), \\
          \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\scid],\attrs)
          \rangle \\
          \trans[\cid] \gets \utrans \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
          \pcreturn \top \\
        }

        \procedure{$\SIGN(\oid,\uid,\scid,\msg,\feval)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,\feval) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\oid,\scid,\Sig,\msg,\feval) \rbrace \\
          \pcreturn \Sig \\
        }

        \procedure{$\OPEN(\oid,\Sig,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\msg,\feval)
          \in \SIG[\uid] \\
%          \textrm{Parse}~\Sig~\textrm{as}~(\sig,\yeval,\ceval) \\
          (\yinsp,\iproof) \gets
          \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
          \pcif \CSIG[\Sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
            \feval$} \\
          \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b}) \\
          \pcind (\yinsp',\iproof') \gets
          \Open(\PRVOK[\oid],\IK[\siid],\\
          \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
          \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
          \pcreturn (\yinsp,\iproof)
        }

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\oid,\scid,\msg,\feval)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
    \pcif \feval \notin \famfeval: \pcreturn 0 \\
    \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
    (\Sig = (\sig,\yeval,\ceval)) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,
    \feval) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
    \pcfor \cid \in \scid \pcdo: \\
    \pcind \textrm{Let}~\scred^{\cid}~\textrm{be the credentials used to obtain}
    ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,\fissue^{\cid}),\cdot)\\
    \pcind \pcif \fissue^{\cid}(\UK[\uid],\scred^{\cid},\ATTR[\cid]) = 0: \pcreturn 1 \\
    (\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\CRED[\scid],\msg) \\
    \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
    (\yinsp,\iproof) \gets \Open(\PRVOK[\gid],\PUBIK[\scid],\Sig,\msg,\feval) \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
    = 0~\lor \\
    \pcind \yinsp \neq \finsp^\gid((\yeval,\yeval^1),\UK[\uid],\CRED[\scid],\msg)): \\
    \pcind \pcreturn 1 \\
    \pcreturn 0
  }  
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

\paragraph{Anonymity.} %
Informally, anonymity must capture two requirements: (1) interactive credential
issuance protocols do not leak any information about the user requesting them;
and (2) signatures do not leak any information about the signer. In both cases,
any leakage must be limited to whatever the user decides to reveal, for
instance, through arbitrary predicates on the attributes of the credentials used
for issuance and signing. We follow a simulation-based approach to capture this.
Basically, the adversary is challenged to distinguish between real and ideal
executions. In both worlds, the adversary can generate and corrupt honest users,
issuers, and openers. Then, in the real world, the adversary has access to
oracles that allow requesting credentials on behalf of honest users, create
signatures by honest users, and open signatures by honest users. In the ideal
world, these three oracles are replaced by simulated counterparts, which produce
outputs independent of the users' secrets. This formulation is given in
\figref{fig:exp-uas-simanon}, where $\Osimanon = (\lbrace\HU,\CU\rbrace\GEN,
\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\WREG)$.

@@

\begin{definition}{(Anonymity of \UAS)}
  \label{def:anonymity-uas}  
  We define the advantage \AdvSimAnon of $\adv$ against \ExpSimAnonb as
  $\AdvSimAnon=|\Pr\lbrack\ExpSimAnono(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpSimAnonz(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme satisfies simulatable anonymity if there exists simulators
  \SIMSETUP, \SIMOBTAIN, \SIMSIGN and \SIMOPEN such that, for any p.p.t.
  adversary $\adv$, \AdvSimAnon is a negligible function of $1^\secpar$.
\end{definition}

\iffalse
In addition to the considerations made for \GSAC (see \secref{ssec:model-gsac}),
in our notion of anonymity for \UAS,
in order to prevent trivial wins by the adversary, we have to restrict that the
signing evaluation function outputs the same value for both user-credentials
pairs. Very interestingly, since our opening functionality does not
(necessarily) output the identity of the signer, \uline{we can even allow the
  adversary to open challenge signatures, as long as they produce the same
  output}. Other than this, the overall approach is similar: as
in group signatures and anonymous credentials, the adversary asks for challenge
signatures from either one of two honest users and credential sets -- bit $b$,
unkown to the adversary, defining which one is used. Note that the adversary
also has to pick a signature valuation function \feval, as well as an opener
(passed as arguments to the \SIGN and \CHALb oracles). The formal specification
of the anonymity game is given in \figref{fig:exp-uas-anonb}, where $\Oanon
\gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace
\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$

\begin{figure}[htp!]
  \centering
  \procedure[linenumbering]{$\ExpAnonb(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     b^* \gets \adv^{\Oanon} (\status,\parm) \\
     \pcreturn b^*
  }
  \caption{Anonymity experiment for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure}

\begin{definition}{(Anonymity of \UAS)}
  \label{def:anonymity-uas}  
  We define the advantage \AdvAnon of $\adv$ against \ExpAnonb as
  $\AdvAnon=|\Pr\lbrack\ExpAnono(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpAnonz(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme satisfies anonymity if, for any p.p.t. adversary $\adv$,
  \AdvAnon is a negligible function of $1^\secpar$.
\end{definition}

>>>>

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given global system
  parameters \parm, and function \finsp, an opener runs \OKeyGen to generate
  its opening key pair. The function \finsp defines the type of utility that
  will be extractable from signatures.
\item[$\UKeyGen(\parm) \rightarrow \usk$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle
  \Obtain(\usk,\ipk,\scred,\attrs),
  \Issue(\isk,\sipk,\attrs))
  \rangle \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.] %
  This interactive protocol lets a user with key \usk running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of credentials \scred,
  each with a matching issuer key in \sipk.
  The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential.
\item[$\Sign(\usk,\opk,\scred,\msg,\feval) \rightarrow (\sig,\yeval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \scred, a message \msg and evaluation
  function \feval, returns signature \sig, and a plaintext value \yeval. For
  readability, we use \Sig to denote the tuple $(\sig,\yeval)$.
\item[$\Verify(\opk, \sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\Sig,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $\Sig=
  (\sig,\yeval)$ over message \msg and evaluation function \feval,
  generated using credentials issued by the issuers with public keys in \sipk.
  If \Sig is valid, the function outputs a value $\yinsp$.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

\begin{description}
\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\attrs_{\scred},\scred)$.]
  Receives an $\langle \Obtain, \Issue \rangle$ transcript, and returns the
  credentials (if any) and their attributes that were involved
  in the request. It clearly needs an honest issuer as, otherwise, the
  transcripts won't be available. Consequently, we only use it to define the
  properties that require an honest issuer.
\item[$\ExtractSign(\oid,\siid,\Sig,\msg,\feval) \rightarrow (\usk,
  \scred,\attrs_{\scred},\yeval^1,\yinsp)$.] Receives a signature \Sig,
  as well as the opener identifier \oid, and the identifiers of all issuers of
  the credentials used to produce the signature over \msg, and for \feval. It
  outputs the user secret key and credentials (with their attributes) used to
  generate the signature, and the value returned by the opening fuction.
\item[$\IdentifyCred(\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
  issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
  Otherwise, it returns $0$. In order to be meaningful, this requires that,
  for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
  \IdentifyCred return $1$.
\item[$\IdentifyUK(\uid,\usk)$.] Returns $1$ is \usk is {\uid}'s secret key.
  This is trivial for honest users, for which there must be a one-to-one
  relationship between {\uid}s and {\usk}s. For corrupt users, \IdentifyUK has
  to iterate through the $\langle\Obtain,\Issue\rangle$ transcripts associated
  to \uid, extract the used secret key, and check if there is a match. Note that
  this does not guarantee that there will be only one \usk per corrupt \uid,
  though. Also, when used for corrupt users, this can only be used when the
  issuer is honest, as transcripts are needed. 
\end{description}

@@

        \procedure{$\OBTISS(\cid,\uid,\iid,\attrs,\scid)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \HI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
          %\pcif \exists \iid' \in \ISR[\scid]~\st~\iid' \notin \HI: \pcreturn \bot \\
          %\pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot:
          \langle \cred, \utrans \rangle \gets
          \langle \Obtain(\UK[\uid],\CRED[\scid],\attrs), \\
          \hspace*{60pt} \Issue(\PRVIK[\iid],\ISR[\scid],\attrs)
          \rangle \\
          \trans[\cid] \gets \utrans \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
          \pcreturn \top \\
        }

        \procedure{$\ISSUE(\cid,\uid,\iid,\attrs,\siid)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\          
          \pcif \iid \notin \HI: \pcreturn \bot \\
          %\pcif \exists \iid' \in \ISR[\scid] \notin \HI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, 
          \Issue(\PRVIK[\iid],\siid,\attrs) \rangle \\
          \trans[\cid] \gets \utrans \\
          \CRED[\cid] \gets (\uid, \cdot, \iid, \attrs, \cdot, \siid) \\
          \pcreturn \top \\          
        }

        \procedure{$\SIGN(\oid,\uid,\scid,\msg,\feval)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\
          \pcif \exists \cid \in \scid~\suchthat~\cid \in \CRED~\land \\
          \pcind \exists \cid' \in \scid~\suchthat~\cid' \in \CCRED: \pcreturn \bot \\
          \Sig \gets \Sign(\UK[\uid],\PUBOK[\oid],\CRED[\scid],\msg,\feval) \\
          \Yeval=(\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\CRED[\cscid],\msg) \\
          \SIG[\uid] \gets \SIG[\uid] \cup
          \lbrace (\oid,\scid,\Sig,\Yeval,\msg,\feval) \rbrace \\
          \pcreturn \Sig \\
        }

        \procedure{$\OPEN(\oid,\Sig,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\Sig,\Yeval,\msg,\feval)
          \in \SIG[\uid] \\
%          \textrm{Parse}~\Sig~\textrm{as}~(\sig,\yeval,\ceval) \\
          (\yinsp,\iproof) \gets
          \Open(\PRVOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) \\
          \pcif \CSIG[\Sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\Sig]$ as $(\oid,\cuid_b,\scid_b,
            \Yeval,\msg,\feval$} \\          
          \hspace*{83pt}\cuid_{1-b},\cSig_{1-b},\scid_{1-b},
          \TYeval) \\
          %\pcind \pcif \yeval^1 \neq \tyeval^1: \pcreturn \bot \\          
          \pcind (\tyinsp,\tiproof) \gets
          \Open(\PRVOK[\oid],\IK[\siid],\\
          \hspace*{107pt} \cSig_{1-b},\msg,\feval) \\
          \pcind \pcif \tyinsp \neq \yinsp: \pcreturn \bot \\
          \pcreturn (\yinsp,\iproof)
        }

@@

        \procedure{$\OBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\suchthat~\cid' \in \CRED~\land \\
          \pcind \exists \cid'' \in \scid~\suchthat~\cid'' \in \CCRED: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot \lor \CCRED[\cid] \neq \bot: \pcreturn \bot \\
          %\pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\CRED[\scid],\attrs),\adv \rangle \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
          \pcreturn \top \\
        }

        \procedure{$\OBTCHALb(\cid,\iid,\cuid_{0,1},\cscid_{0,1},\attrs)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \pcif \pcfor d \in \bin,~ \exists \cid' \in \cscid_d~\suchthat~\cid'
          \in \CRED~\land \\
          \pcind \exists \cid'' \in \cscid_d~\suchthat~\cid'' \in \CCRED:
          \pcreturn \bot \\
          \textrm{Parse}~\PUBIK[\iid]~\textrm{as}~((\cdot,\fissue),\cdot) \\
          \pcif \fissue(\UK[\cuid_0],\cscid_0,\attrs) \neq
          \fissue(\UK[\cuid_1],\cscid_1,\attrs) \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\cuid_b],\PUBIK[\iid],\CRED[\scid_b],\attrs),\adv \rangle \\
          \CCRED[\cid] \gets (\cuid_b, \cred, \iid, \attrs, \scid_b, \siid) \\
          \pcreturn \top \\
        }

        \procedure{$\CHALb(\oid,\cuid_{0,1},\cscid_{0,1},\msg,\feval)$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \oid \in \CO: \pcreturn \bot \\
          \pcif \feval \notin \famfeval: \pcreturn \bot \\          
          \Yeval = (\yeval^0,\yeval^1) \gets \feval(\UK[\cuid_0],\CRED[\cscid_0],
          \msg) \\
          \TYeval = (\tyeval^0,\tyeval^1) \gets
          \feval(\UK[\cuid_1],\CRED[\cscid_1],\msg) \\
          \pcif \yeval^0 \neq \tyeval^0: \pcreturn \bot \\
          \pcif \PUBIK[\cscid_0] \neq \PUBIK[\cscid_1]: \pcreturn \bot \\
          \cSig_b \gets \Sign(\UK[\cuid_b],\PUBOK[\oid], \\
          \hspace*{71pt}\CRED[\cscid_b],\msg,\feval) \\
          \cSig_{1-b} \gets \Sign(\UK[\cuid_{1-b}],\PUBOK[\oid], \\
          \hspace*{80pt}\CRED[\cscid_{1-b}],\msg,\feval) \\          
          \CSIG[\cSig_b] \gets 
          \lbrace (\oid,\cuid_b,\cscid_b,\Yeval,\msg,\feval,\\
          \hspace*{74pt}\cuid_{1-b},\cSig_{1-b},\cscid_{1-b},\TYeval)\rbrace \\
          \pcreturn \cSig_b
        }

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\oid,\scid,\msg,\feval)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
    \pcif \feval \notin \famfeval: \pcreturn 0 \\
    \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
    (\Sig = (\sig,\yeval)) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,
    \feval) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
    \pcfor \cid \in \scid \pcdo: \\
    \pcind \textrm{Let}~\scred^{\cid}~\textrm{be the credentials used to obtain}
    ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,\fissue^{\cid}),\cdot)\\
    \pcind \pcif \fissue^{\cid}(\UK[\uid],\scred^{\cid},\ATTR[\cid]) = 0: \pcreturn 1 \\
    (\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\CRED[\scid],\msg) \\
    \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
    (\yinsp,\iproof) \gets \Open(\PRVOK[\gid],\PUBIK[\scid],\Sig,\msg,\feval) \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
    = 0~\lor \\
    \pcind \yinsp \neq \finsp^\gid((\yeval,\yeval^1),\UK[\uid],\CRED[\scid],\msg)): \\
    \pcind \pcreturn 1 \\
    \pcreturn 0
  }  
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

\paragraph{Anonymity.} %
\iffalse
Informally, anonymity must capture two requirements: (1) interactive credential
issuance protocols do not leak any information about the user requesting them;
and (2) signatures do not leak any information about the signer. In both cases,
any leakage must be limited to whatever the user decides to reveal, for
instance, through arbitrary predicates on the attributes of the credentials used
for issuance and signing. We follow a simulation-based approach to capture this.
Basically, the adversary is challenged to distinguish between real and ideal
executions. In both worlds, the adversary can generate and corrupt honest users,
issuers, and openers. Then, in the real world, the adversary has access to
oracles that allow requesting credentials on behalf of honest users, create
signatures by honest users, and open signatures by honest users. In the ideal
world, these three oracles are replaced by simulated counterparts, which produce
outputs independent of the users' secrets. This formulation is given in
\figref{fig:exp-uas-simanon}, where $\Osimanon = (\lbrace\HU,\CU\rbrace\GEN,
\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\WREG)$.

@@

\begin{definition}{(Anonymity of \UAS)}
  \label{def:sign-anonymity-uas}  
  We define the advantage \AdvSimAnon of $\adv$ against \ExpSimAnonb as
  $\AdvSimAnon=|\Pr\lbrack\ExpSimAnono(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpSimAnonz(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme satisfies simulatable anonymity if there exists simulators
  \SIMSETUP, \SIMOBTAIN, \SIMSIGN and \SIMOPEN such that, for any p.p.t.
  adversary $\adv$, \AdvSimAnon is a negligible function of $1^\secpar$.
\end{definition}
\fi

In addition to the considerations made for \GSAC (see \secref{ssec:model-gsac}),
in our notion of anonymity for \UAS,
in order to prevent trivial wins by the adversary, we have to restrict that the
signing evaluation function outputs the same value for both user-credentials
pairs. Very interestingly, since our opening functionality does not
(necessarily) output the identity of the signer, \uline{we can even allow the
  adversary to open challenge signatures, as long as they produce the same
  output}. Other than this, the overall approach is similar: as
in group signatures and anonymous credentials, the adversary asks for challenge
signatures from either one of two honest users and credential sets -- bit $b$,
unkown to the adversary, defining which one is used. Note that the adversary
also has to pick a signature valuation function \feval, as well as an opener
(passed as arguments to the \SIGN and \CHALb oracles). The formal specification
of the anonymity game is given in \figref{fig:exp-uas-anonb}, where
$\OIssAnon \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,
\OO\rbrace\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\OBTCHALb)$, and $\OSigAnon
\gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace
\CORR,\OBTAIN,\WREG,\SIGN,\OPEN,\CHALb)$.

\begin{figure*}[htp!]
  \centering
  \scalebox{0.9}{
    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpIssAnonb(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\OIssAnon} (\status,\parm) \\
        \pcreturn b^*
      }
    \end{minipage}

    \begin{minipage}[t]{0.5\textwidth}
      \procedure[linenumbering]{$\ExpSigAnonb(1^\secpar)$}{%
        \parm \gets \Setup(1^\secpar) \\
        b^* \gets \adv^{\OSigAnon} (\status,\parm) \\
        \pcreturn b^*
      }
    \end{minipage}
  }
  \caption{Issuance and signature anonymity experiments for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure*}

\begin{definition}{(Issuance anonymity in \UAS)}
  \label{def:issue-anonymity-uas}  
  We define the advantage \AdvIssAnon of $\adv$ against \ExpIssAnonb as
  $\AdvIssAnon=|\Pr\lbrack\ExpIssAnono(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpIssAnonz(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme satisfies issuance anonymity if, for any p.p.t. adversary
  $\adv$, \AdvIssAnon is a negligible function of $1^\secpar$.
\end{definition}

\begin{definition}{(Signature anonymity in \UAS)}
  \label{def:sign-anonymity-uas}  
  We define the advantage \AdvSigAnon of $\adv$ against \ExpSigAnonb as
  $\AdvSigAnon=|\Pr\lbrack\ExpSigAnono(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpSigAnonz(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme satisfies signature anonymity if, for any p.p.t. adversary
  $\adv$, \AdvSigAnon is a negligible function of $1^\secpar$.
\end{definition}
